Distinguishing NFW and Isothermal Density Profiles with Gravitational Lensing

### 2018-04-17 paper.tex
Updates to article

Tangential shear at radius R
\begin{equation}
    \gamma(R) = \overline{\kappa}(R) - \kappa(R)
\end{equation}

@@

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many background galaxies
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test?
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at?

@@

50 gals/square arcminute
5 arcminutes
z_L = 0.3
z_S = 1
M_halo = 10^15 solar masses
instrinsic ellipticity from gaussian with width 0.2

>>>>

Tangential shear at radius R
\begin{equation}
    \gamma_t(R) = \overline{\kappa}(R) - \kappa(R)
\end{equation}

\[\gamma_1 = -\gamma_t \cos{2\phi}\]
\[\gamma_2 = -\gamma_t \sin{2\phi}\]

@@

We switch dependence from $\sigma^2$ to $M_{200}$ with:

\begin{equation}
    r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}
\end{equation}

\begin{equation}
    \sigma^2 = \frac{G M_{200}}{2 \left(
        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
        - r_c \arctan \left(
            \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {r_c}^3}
        \right)
    \right)}
\end{equation}

$M_{200}$ is defined as:
\begin{equation}
    M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi r_{200}^3
\end{equation}

\subsection{Current plan}
\begin{itemize}
    \item Calculate tangential shear and deflection angle for NFW and SIS
    \item Consider single foreground lens halo with many background galaxies
    \item How to arrange and distribute background halos?
    \begin{itemize}
        \item Initial ellipticity
        \item angular density on sky
        \item sizes
    \end{itemize}
    \item Apply shear and deflection angle to background galaxies
    \item Attempt to fit both profiles, subtracting intrinsic shear, see if the fit is distinguishable
    \item How many foreground halos to test? - start with 1
    \item What redshift is $\rho_\mathrm{crit}$ evaluated at? - at halo redshift

@@

50 gals/square arcminute
5 arcminutes
$z_L = 0.3$
$z_S = 1$
$M_halo = 10^15$ solar masses
instrinsic ellipticity from gaussian with width 0.2
